---
title: "tier Classification with Ranger model Machine Learning"
output: html_document
date: "`r Sys.Date()`"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(dplyr.summarise.inform = FALSE)
getwd()
```

```{r, message=FALSE, echo=FALSE, warning = FALSE}
library(tidyverse)
library(gridExtra)
library(caret)
library(fmsb)
library(arules)
library(patchwork)
library(ranger)
create_beautiful_radarchart <- function(data, color = "#00AFBB", 
                                        vlabels = colnames(data), vlcex = 0.7,
                                        caxislabels = NULL, title = NULL, ...){
  radarchart(
    data, axistype = 1,
    # Customize the polygon
    pcol = color, pfcol = scales::alpha(color, 0.5), plwd = 2, plty = 1,
    # Customize the grid
    cglcol = "grey", cglty = 1, cglwd = 0.8,
    # Customize the axis
    axislabcol = "grey", 
    # Variable labels
    vlcex = vlcex, vlabels = vlabels,
    caxislabels = caxislabels, title = title, ...
  )
}

```

This file contains an exploration of the classification analysis for Pick/Ban Rate, Win Rate, and KDA, as attempts to predict tier. 

```{r, message=FALSE}

leaguedf <- read_csv('S13LeagueOfLegendsData.csv', col_types=cols()) %>% 
  rename(winr = "Win %", pick = 'Pick %', ban = 'Ban %', roler = 'Role %') %>%
  mutate(pbr = pick + ban, tier = Tier) %>%
  select(-c(1,2,5, 6,7,10,11))


head(leaguedf, 5)
```
#### Key for Reference
- tier: tier of champion
- winr: winrate of champion
- KDA: Kill/Death/Assist Ratio, $\frac{\text{kills} + \text{assists}}{\text{deaths}}$
- pbr: Pick Ban Rate, Pick rate + Ban rate
- Class: Class of fighter, categorical choice
- ROLE: role that data was collected for
- roler: Percentage of games that were played for this champion on this role
- patch: Patch that data was collected from


```{r}

leaguedf$tier <- factor(leaguedf$tier, levels=c('D', 'C', 'B', 'A', 'S', 'God'), ordered=TRUE)
plot1 <- ggplot(data=leaguedf) + 
  geom_boxplot(mapping = aes(x = tier, y=winr, fill=tier)) +
  ggtitle('Win Rate and tier') +
  ylab('Win Rate') + 
  theme(legend.position='none') +
  scale_fill_brewer(palette="BuPu")

plot2 <- ggplot(data = leaguedf) + 
  geom_boxplot(mapping = aes(x= tier, y=pbr, fill=tier)) +
  ggtitle('Pick/Ban Rate and tier') +
  ylab('Pick/Ban Rate') + 
  theme(legend.position='none') + 
  scale_fill_brewer(palette="Dark2")
  
  
grid.arrange(plot1, plot2, ncol=2)


```



```{r}
ggplot(data=leaguedf) + 
  geom_bar(mapping=aes(x=tier, fill=tier)) + 
  scale_fill_brewer('viridis') + 
  theme(legend.position = 'none') + ylab("Number of Observations") 

```

```{r}
tier_stats <- leaguedf %>%
  group_by(tier) %>% 
  summarize(KDA = median(KDA), pbr = median(pbr), wr=median(winr))
tier_stats$tier <-  factor(tier_stats$tier, levels=c('D', 'C', 'B', 'A', 'S', 'God'), ordered=TRUE)
tier_stats <- as_tibble(tier_stats) %>% column_to_rownames(var = "tier") 
  # statistics wanted by tier, and change row name to tier

max_min <- data.frame(KDA = c(0, 5), pbr=c(0,1), wr=c(0,1)) #Formatting data for radar chart
rownames(max_min) <- c("Max", "Min")

radar_frame <- rbind(max_min, tier_stats) #final frame for radar chart

#The next two lines split the area for the radar charts
op <- par(mar = c(1.5,1.5,1.5,1.5)) 
#Split into 6 pieces
par(mfrow = c(2,3))

#Color for each tier
colors = c("#D95F45", "#D9B245", "#62D945", "#45D9AA", "#45A6D9", "#7145D9")

#Title for each chart
titles = c("A", "B", "C", "D", "S", "God")

#make them
for (i in 1:6) {
  create_beautiful_radarchart(data = radar_frame[c(1,2, i+2), ],
                              color = colors[i], title = titles[i]
                              )
} #TODO: FIgure out why its wrong
par(op)
```

p.s. I think spider plot is cooler name than radar chart.



## Thoughts

- For higher tiers, such as God, S, and A, it seems that pick ban rate significantly rises.
- For lower tiers, such as D and C, the win rate significantly drops.
- Alone, each of them would likely only do so well to analyze the tiers, but together they seem to be better.
- The number of observations is fairly symmetric with respect to the middle (A/B)

## Moving Forwards
From here on, we will begin classification techniques. The data is overall fairly symmetric with respect to the 


```{r}
set.seed(27)

# Split the data into test/train. We want 75% for training, and 25% for testing.

inTrain <- createDataPartition(y=leaguedf$tier, p=0.75, list=FALSE) 

leagueTraininit <- leaguedf[ inTrain, ]
leagueTestinit <- leaguedf[ -inTrain, ]

#Verify we did it correct, 0.75*5637 is approx 4225
nrow(leagueTraininit)
```
```{r, eval=TRUE, echo=FALSE}
rf_fit <- readRDS('rf_initial_fit.rds')
```


```{r, eval=FALSE}

rf_fit <- train(as.factor(tier) ~ .,
                data = leagueTraininit,
                method="ranger")

rf_fit
```

```{r, echo=FALSE, eval=FALSE}
saveRDS(rf_fit, "rf_initial_fit.rds")
```

```{r}
rf_pred <- predict(rf_fit, leagueTestinit)

cm <- confusionMatrix(rf_pred, as.factor(leagueTestinit$tier), dnn = c("Prediction", "Actual"))
plt <- as.data.frame(cm$table)
plt$Prediction <- factor(plt$Prediction, levels=rev(levels(plt$Prediction)))

ggplot(plt, aes(Prediction,Actual, fill=Freq)) +
        geom_tile() + geom_text(aes(label=Freq)) +
        scale_fill_gradient(low="white", high="#009194") +
        labs(x = "Actual",y = "Prediction") +
        scale_y_discrete(labels=c('D', 'C', 'B', 'A', 'S', 'God')) +
        scale_x_discrete(labels=c('God', 'S', 'A', 'B', 'C', 'D')) + theme_minimal()


```

```{r, eval=FALSE}
Mode <- function(x) {
  ux <- unique(x)
  ux[which.max(tabulate(match(x, ux)))]
}

Boundarydf = expand.grid(winr = seq(0.4, 0.6, length.out=50), pbr = seq(0, 1, length.out=50), KDA = seq(1, 5, length.out=40), Role = "SUPPORT", `roler` = seq(0.1,1, length.out=10), Patch=c("13_12"), Class=c("Mage", "Support"))
Boundarydf$tier <- predict(rf_fit, Boundarydf)
Boundarydf <- Boundarydf %>%
  group_by(winr, pbr) %>%
  summarize(tier = Mode(tier)) %>%
  ungroup()

write.csv(Boundarydf, "BoundaryFrame.csv")


```

```{r, echo=FALSE}
Boundarydf <- read_csv("BoundaryFrame.csv")
```

```{r, eval=TRUE}

leaguedf %>% filter(Role=="SUPPORT", Patch=="13_12", Class == "Mage" | Class == "Support")
leaguedf %>% filter(Role=="SUPPORT", Patch=="13_12", Class == "Mage" | Class == "Support") %>%
  ggplot(mapping=aes(x=winr, y=pbr, fill=tier)) + geom_raster(data=Boundarydf, alpha=0.5) + geom_point(shape=21, mapping=aes(size=KDA), alpha=0.75) + theme_minimal() + xlab('Win Rate') + ylab('Pick Ban Rate') + ggtitle('Boundary Plot for Support in Patch 13.12')

```

```{r}

leagueTestinit$pred <- rf_pred
leagueTestinit %>%
  mutate(correct = (pred == tier)) %>% rowwise() %>%
  filter(!(Class == 'NULL')) %>%
  group_by(Role, Class) %>%
  summarize(accuracy = sum(correct)/ n()) %>%
  ungroup() %>% complete(Role, Class, fill=list(NULL)) %>%
  ggplot() + geom_tile(mapping = aes(x = Role, y = Class, fill=accuracy )) + 
    ggtitle("Heatmap for Accuracy by Class/Role") + 
    scale_fill_continuous(na.value="darkred", breaks=c(0,0.5,1), labels=c("0%", "50%", "100%"), limits=c(0,1))
```

- From the boundary plot and confusion matrix, we can see our model is pretty good at sorting through God, S, and A tiers, but worse at B and C.
- We can tell from the boundary plot that Pick Ban Rate is very important in telling whether or not a champion is god tier, since almost all of the area above 50% pick ban rate is designated to God tier.


### Preprocessing Data
```{r}
#First we want to create extra data.




leaguedf_final <- leaguedf %>%
  mutate(Patch = as.numeric(str_replace(Patch, '(.*?)_(.*?)', ''))) #This turns patch to numeric 


inTrain <- createDataPartition(y=leaguedf_final$tier, p=0.75, list=FALSE) 

leagueTrain <- leaguedf_final[ inTrain, ]
leagueTest <- leaguedf_final[ -inTrain, ]


```

### Hypertuning Model on Preprocess Data
This will take a long time, so please be patient if you run this yourself.
```{r, echo=FALSE}
fit <- readRDS("RangerFITwPatch.rds")
```

```{r, eval=FALSE}
grid <- expand.grid(mtry = c(6,9,12), splitrule=c("extratrees", "gini"), min.node.size=c(1,3,6,10))

fitControl <- trainControl(method='CV', number = 5, verboseIter=FALSE)

fit <- train(as.factor(tier)~.,
             data=leagueTrain,
             method="ranger",
             tuneGrid=grid,
             trControl = fitControl, importance="impurity"
)

```

```{r}
fit$finalModel 
```

```{r}
#This model is not used for classification purposes, but for finding p-values!
ranger_fit <- ranger(formula = tier ~ .,
                       data = leagueTrain,
                       num.trees = 500,
                       mtry = 7,
                       min.node.size = 1,
                       importance = "impurity_corrected",
                       splitrule = "extratrees",
)
```

```{r}
setwd('../ClassificationML')
saveRDS(fit, "RangerFITwPatch.rds")
```

```{r}
paste("Initial accuracy is: ", round(sum(leagueTestinit$tier == predict(rf_fit, leagueTestinit)) / length(leagueTestinit$tier), 4)*100, '%', sep='')
paste("Final accuracy is: ", round(sum(leagueTest$tier == predict(fit, leagueTest)) / length(leagueTest$tier), 4)*100, '%', sep='')


fit$results %>%  
  mutate(mtry = as.character(mtry), min.node.size = as.character(min.node.size)) %>%
  mutate(mtry = factor(mtry, levels=c("6", "9", "12", "15"), ordered=TRUE),
         min.node.size = factor(min.node.size, levels = c("1","3", "6", "10"), ordered=TRUE)) %>%
  ggplot() + geom_tile(mapping = aes(x=mtry, y=min.node.size, fill=Accuracy)) + facet_wrap(splitrule ~.) + ggtitle("Accuracy vs. Kappa for each value")
```

### Recreation of Charts

```{r, fig.width = 12}
ImpFrame <- varImp(fit)[1] %>%
  as_tibble(rownames="VariableName") 
ImpFrame <- ImpFrame$importance %>% as_tibble(rownames="VariableName") %>%
  mutate(VariableName = case_when(
    grepl('Class', VariableName, fixed = TRUE) ~ 'Class',
    grepl("Role", VariableName, fixed = TRUE) ~'Role',
    TRUE ~ VariableName
  ))  %>%
  group_by(VariableName) %>%
  summarize(Overall = sum(Overall)) %>%
  arrange(Overall) %>%
  mutate(VariableName = as.factor(VariableName))


plot1 <- ggplot(varImp(fit)) + 
    geom_bar(mapping = aes(x = Feature, y = Importance, fill=Importance), stat = "identity", position = "dodge")  +
    ylab("Variable Importance") +
    xlab("") +
    ggtitle("Importance by Feature") +
    scale_fill_gradient(low = "red", high = "blue") + 
  theme(legend.position = "none")

plot2 <- ggplot(ImpFrame) + 
  geom_bar(mapping = aes(x = fct_reorder(VariableName, Overall), y = Overall, fill= Overall), stat = "identity", position = "dodge") +
  ylab("Variable Importance") + 
  xlab("") + 
  ggtitle("Importance grouped by Column") + 
  scale_fill_gradient(low = "red", high = "blue") + 
  coord_flip() + 
  labs(fill = "Importance")
plot1 & plot2
```


```{r, eval=FALSE}

finalBoundarydf = expand.grid(winr = seq(0.4, 0.6, length.out=50), 
                            pbr = seq(0, 1, length.out=50), 
                            KDA = seq(1, 5, length.out=40), 
                            Role = "SUPPORT", 
                            `roler` = seq(0.1,1, length.out=10), 
                            Patch = c(12), 
                            Class = c("Mage", "Support"))


finalBoundarydf$tier <- predict(fit, finalBoundarydf) #Why does it say Class not found?
finalBoundarydf <- Boundarydf %>%
  group_by(winr, pbr) %>%
  summarize(tier = Mode(tier)) %>%
  ungroup()

write.csv(Boundarydf, 'FinalBoundarydf.csv')

```

```{r, echo=FALSE}
finalBoundarydf <- read_csv("FinalBoundarydf.csv")
```

```{r, eval=TRUE, fig.height=5, fig.width=12}
plot1 <- leaguedf %>%
  filter(Role=="SUPPORT", Patch=="13_12", Class == "Mage" | Class == "Support") %>%
  ggplot(mapping=aes(x=winr, y=pbr, fill= tier)) + 
    geom_raster(data=Boundarydf, alpha=0.5) + 
    geom_point(shape=21, mapping=aes(size=KDA), alpha=0.75) + 
    theme_minimal() + 
    xlab('Win Rate') + 
    ylab('Pick Ban Rate') + 
    ggtitle('Pre tuning') 

plot2 <- leaguedf %>% 
  filter(Role=="SUPPORT", Patch=="13_12", Class == "Mage" | Class == "Support") %>%
  ggplot(mapping=aes(x=winr, y=pbr, fill= tier))+ 
    geom_raster(data=finalBoundarydf, alpha=0.5) + 
    geom_point(shape=21, mapping=aes(size=KDA), alpha=0.75) + 
    theme_minimal() + 
    xlab('Win Rate') + 
    ylab('') + 
    ggtitle('Post Tuning')

patch <- plot1 +  plot2 & theme(legend.position="bottom")
patch + plot_layout(ncol=2,guides="collect") + plot_annotation(title="Boundary Plots for Support on Patch 13.12", theme = theme(plot.title = element_text(size = 20)))
```

```{r}
rf_pred <- predict(fit, leagueTest)

cm <- confusionMatrix(rf_pred, as.factor(leagueTest$tier), dnn = c("Prediction", "Actual"))
plt <- as.data.frame(cm$table)
plt$Prediction <- factor(plt$Prediction, levels=rev(levels(plt$Prediction)))

ggplot(plt, aes(Prediction,Actual, fill=Freq)) +
        geom_tile() + geom_text(aes(label=Freq)) +
        scale_fill_gradient(low="white", high="#009194") +
        labs(x = "Actual",y = "Prediction") +
        scale_y_discrete(labels=c('D', 'C', 'B', 'A', 'S', 'God')) +
        scale_x_discrete(labels=c('God', 'S', 'A', 'B', 'C', 'D')) + theme_minimal()


```


```{r}
leagueTest$pred <- rf_pred
leagueTest %>%
  mutate(correct = (pred == tier)) %>% rowwise() %>%
  filter(!(Class == 'NULL')) %>%
  group_by(Role, Class) %>%
  summarize(accuracy = sum(correct)/ n()) %>%
  ungroup() %>% complete(Role, Class, fill=list(NULL)) %>%
  ggplot() + geom_tile(mapping = aes(x = Role, y = Class, fill=accuracy )) + 
    ggtitle("Heatmap for Accuracy by Class/Role") + 
    scale_fill_continuous(na.value="darkred", breaks=c(0,0.5,1), labels=c("0%", "50%", "100%"), limits=c(0,1))
```


```{r, eval = F}
importance_pvalues(ranger_fit, 
                   method= c("altmann"),
                   formula = tier ~.,
                   data = leaguedf_final)
```

       importance     pvalue
Class   57.14298 0.00990099
Role    90.31376 0.00990099
winr   233.60722 0.00990099
roler  349.44834 0.00990099
KDA    142.37590 0.00990099
Patch   37.74229 0.00990099
pbr    558.14357 0.00990099

```{r}
#Cluster Analysis I added after cause im reading a textbook on a plane.
leaguedf %>%
  ggplot(mapping = aes(x = pbr, y = winr)) + geom_point(mapping = aes(color = tier), alpha = 1, size =0.5) + xlim(0, 0.3)

```